### 2010-09-14 proposal/preProposal.tex
minor
Version presented/sent as pre-proposal

The human members of our team are Diana Hidalgo, Sarah Nguyen, and
Jason Yosinski.  The sole robotic member of our team is a 9 DoF
starfish shaped robot from Hod Lipson's lab.

@@

\edit{todo}

2.Problem statement and motivation. A statement of the problem, issue,
or task that you’re interested in studying, and why it is interesting
or important.

@@

\edit{todo}

3.I/O Specification. A clear, concise description of what the final
system will do in terms of I/O behavior: What will it take in, and
what it will produce.

\section{Background reading (optional)}

\edit{todo}

4.Background Reading (OPTIONAL in pre-proposal stage). A list of
relevant readings that you’ll use to gain some background in your
selected topic.

\section{General approach (optional)}

\edit{todo}

5.General Approach (OPTIONAL in pre-proposal stage). A high-level
description of the general approach you’ll use (e.g. heuristic search,
learning, rules, belief networks). This section should have a
subsection entitled “Where’s the AI” where you explicitly articulate
the AI component of this project.

\section{System architecture and work plan (optional)}

\edit{todo}

6.System Architecture and work plan (OPTIONAL in pre-proposal
stage). Explain the main components of the system, how they can be
independently developed and independently tested, and who will do
what.

\section{Data sources (optional)}

\edit{todo}

7.Data sources (OPTIONAL in pre-proposal stage). If your project
involves analyzing real data (e.g. stock market data, sport data, user
behavior), identify potential sources for this data.

\section{Evaluation plans (optional)}

\edit{todo}

8.Evaluation Plans (OPTIONAL in pre-proposal stage). An explicit,
coherent plan for quantitatively and/or qualitatively evaluating the
system. In particular, identify (a) metrics that will help you measure
performance, e.g. time or space to solve a problem, quality of a
solution, or competition or comparison against a standard approach (b)
a simple “toy” problem that you can use for early testing of your
system – something that should be trivial to solve, (b) a “hard” test
case, that will serve as you ultimate test.

>>>>

The human members of our team are Diana Hidalgo, Sarah Nguyen, and
Jason Yosinski.  The sole robotic member of our team is a 9 degree of
freedom starfish shaped robot from Hod Lipson's lab.

@@

There has been much interest in and research surrounding legged
robots.  Such robots exhibit both challenges and opportunities not
present in more traditional wheeled robots.  One of these challenges
is getting the robot to move as quickly and efficiently as possible.
Past research has shown that machine learning methods of optimizing a
walking robot's gait can outperform even the best hand coded gaits
(Chernova 2004).

To this end, we will use machine learning to design a gait for a
quadraped robot, available from Hod Lipson's lab.  We anticipate using
speed and efficiency as metrics for evaluation of the designed gait;
these metrics are presented further in Section~\ref{sec:evaluation}.

%2.Problem statement and motivation. A statement of the problem, issue,
%or task that you’re interested in studying, and why it is interesting
%or important.

@@

Input:

\begin{itemize}
\item Motor encoder position (optional, likely)
\item Motor force feedback (optional, likely)
\item Robot position estimate via external pose estimation system (optional, less likely)
\end{itemize}

\noindent Output:

\begin{itemize}
\item Motor position commands over time
\end{itemize}

\section{Background reading}

We have selected three papers to read for background information on
walking robots. The papers are \emph{An Evolutionary Approach to Gait
  Learning for Four-Legged Robots} by Sonia Chenova and Manuela
Veloso, \emph{Policy Gradient Reinforcement Learning for Fast
  Quadrepedal Locomotion} by Nate Kohl and Peter Stone, and
\emph{Evolving Dynamic Gaits on a Physical Robot} by Viktor Zykov,
Josh Bongard, and Hod Lipson. Hopefully these papers will give us
insights on what kinds of algorithms and techniques to employ in our
learning problem.

\section{General approach}

\subsection{Where's the AI?}

Our general approach is still under development.  We are currently
evaluating the following AI methods for possible inclusion:

\begin{itemize}
\item Optimization (gradient descent, Levenberg-Marquardt, ...)
\item Evolutionary algorithm / Genetic algorithm
\item Reinforcement learning
\item Supervised learning?
\end{itemize}

In addition to these more general methods, the following issues will
also need to be investigated:

\begin{itemize}
\item Reduced dimensionality of parameter space (periodic, symmetric, ...)
\item Parametrized gait vs. non-parametrized gait (?)
\item Geometric constraints
\end{itemize}

\section{System architecture and work plan}

We will be working with a robot that has an on-board computer running Linux. The lower level drivers are in C and we hope to implement the system in Python.

Once we begin working with the robot and have an idea of the algorithm we will use, we will divide the work.

% \section{Data sources (optional)}
% 
% \edit{todo}
% 
% 7.Data sources (OPTIONAL in pre-proposal stage). If your project
% involves analyzing real data (e.g. stock market data, sport data, user
% behavior), identify potential sources for this data.
%

\section{Evaluation plans}
\label{sec:evaluation}

To evaluate our system, we will have three main metrics: speed, number
of failures, and efficiency, which will be compared to its initial
hard-coded walking, and compared to other quadraped robots in the lab:

\begin{itemize}
\item Speed taken to walk a certain distance
\item Number of failures (falling down, getting stuck) over a certain number of attempts
\item Efficiency and power consumption, estimated through a model of the motor
\end{itemize}
